Vaccination

### 2022-03-07 code/vaccination-indicators.Rmd
update

  # Define the combinations of parameters to be tested
  parmsTime <- expand.grid(varPred = c("Unemployment_Benef", "French_nlty", "Asselineau"), 
                           thedate = dates, 
                           predTransform = "discretize_factor", 
                           vaccAge = "by_age", 
                           by.prbs = 0.1, 
                           permutation = FALSE,
                           stringsAsFactors = FALSE)

@@

plotMapVar("Asselineau", byp = 0.1)
plotMapVar("Abstention", byp = 0.1)
plotMapVar("French_nlty", byp = 0.1)

plotMapVar("X1564_OtherInactive_amg_NW", byp = 0.1)

plotMapVar("Stranger", byp = 0.1)

varPred <- "French_nlty"
```

>>>>

  # Define the combinations of parameters to be tested
  parmsTime <- expand.grid(varPred = c("Unemployment_Benef", "Immigrant", "Asselineau"), 
                           thedate = dates, 
                           predTransform = "discretize_factor", 
                           vaccAge = "by_age", 
                           by.prbs = 0.1, 
                           permutation = FALSE,
                           stringsAsFactors = FALSE)

@@

plotMapVar("Asselineau", byp = 0.1)
plotMapVar("Abstention", byp = 0.1)
plotMapVar("Immigrant", byp = 0.1)

plotMapVar("X1564_OtherInactive_amg_NW", byp = 0.1)
```
